[dcpo_demsupport]

### 2020-08-08 paper/dcpo_demsupport.Rmd
facet version, why it isn't work! Very annoying!

## Facet cause NA column, very weird. 
plot_estimate <- map(c("Pooled OLS", "System GMM"), function(aType) {
  filter(df_plot, type == aType) %>%
    dwplot(by_2sd = FALSE) %>%
    relabel_predictors(
      c(
        `plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
        `plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
        `plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
        `plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
        `plm::lag(theta, 1)` = "Democratic Mood(t-1)",
        `plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
        `plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
        `plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
        `plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
        `plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
        `plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
        `plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
        `plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
        `plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
        `plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
        `plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
        `plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
      )
    ) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle(aType) +
    xlab("Coefficient Estimate") +
    theme(axis.title.y = element_blank())
})

library(ggpubr)
ggarrange(plotlist = plot_estimate, common.legend = TRUE)

>>>>

plot_wNA <- dwplot(df_plot, by_2sd = FALSE) %>% 
  relabel_predictors(
    c(
`plm::lag(Vdem_libdem, 1:2)1` = "Democracy(t-1)",
`plm::lag(Libdem_VD, 1:2)1` = "Democracy(t-1)",
`plm::lag(Vdem_libdem, 1:2)2` = "Democracy(t-2)",
`plm::lag(Libdem_VD, 1:2)2` = "Democracy(t-2)",
`plm::lag(theta, 1)` = "Democratic Mood(t-1)",
`plm::lag(SupDem_trim, 1)` = "Democratic Mood(t-1)",
`plm::lag(lg_imp_mdpgdp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(lnGDP_imp, 1)` = "Log GDP per capita(t−1)",
`plm::lag(mdprgdp_grwth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(GDP_imp_grth, 1)` = "GDP per capita Growth(t−1)",
`plm::lag(Region_libdem, 1)` = "Regional democracy(t−1)",
`plm::lag(Libdem_regUN, 1)` = "Regional democracy(t−1)",
`plm::lag(muslism_prop_2010, 1)` = "Percent Muslim (t-1)",
`plm::lag(Pr_Muslim, 1)` = "Percent Muslim (t-1)",
`plm::lag(dependence_pc_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(Res_cp_WDI_di, 1)` = "Resource Dependence(t−1)",
`plm::lag(sigma, 1)` = "Democratic Mood Polarization(t-1)"
    )
  ) +
  geom_vline(xintercept = 0,
             colour = "grey80",
             linetype = 2) +
  theme_minimal() +
  ggtitle("Dependent Variable: Level of Democracy") +
  xlab("Coefficient Estimate") +
  theme(axis.title.y = element_blank()) + 
  facet_wrap(~ type)
